Benchmarks

### 2012-10-24 docs/roadmap/benchmarks.tex
Allowed splits for the 3 shapes.

\input{style.sty}

\title{Benchmarks}
\begin{document}
\maketitle
\pagestyle{headings}

@@

% --------------------------------------------------------------------------------
\subsubsection*{Intermediate results}
\begin{center}\begin{tabular}{cclrrr} \toprule
\bf Matrix & \bf Block & \bf Comment & \bf R(ms) & \bf T(ms) & \bf P(ms) \\ \midrule
1024 & 32 & CPU baseline & 1965.63 & 1191.13 & 6069.66 \\
1024 & 32 & GPU baseline & 838.67 & 499.87 & 516.82 \\
1024 & 32 & GPU sync improved & 642.37 & 316.40 & 343.29 \\
2048 & 32 & CPU baseline & 27229.28 & 15296.09 & 57323.04 \\
2048 & 32 & GPU P 32 blocks & 2864.27 & 1427.21 & 2096.34 \\
\bottomrule \end{tabular} \\[4pt]
Best timings for R=rectangle, T=triangle, P=parallelogram\footnote{$\le 32$ blocks on my GPU to prevent deadlock}
\end{center}

@@

% --------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{bibliography.bib}
\end{document}

>>>>

%\input{style.sty}

%\title{Benchmarks}
%\begin{document}
%\maketitle
%\pagestyle{headings}

\newpage
\section{Benchmarks}

@@

% --------------------------------------------------------------------------------
\subsubsection*{Intermediate results}
\begin{center}\begin{tabular}{cclrrr} \toprule
\bf Matrix & \bf Block & \bf Comment & \bf R(s) & \bf T(s) & \bf P(s) \\ \midrule
1024 & 1 & CPU					& 1.965		& 1.191		& 6.069 \\
2048 & 1 & CPU					& 27.229		& 15.296		& 57.323 \\
4096 & 1 & CPU					& 			& 177.608	&  \\
1024 & 32 & GPU baseline			& 0.838		& 0.500		& 0.516 \\
1024 & 32 & GPU sync improved		& 0.642		& 0.316		& 0.343 \\
2048 & 32 & GPU P $\le32$ blocks		& 2.864		& 1.427		& 2.096 \\
4096 & 32 & GPU 8 splits				& timeout		& 9.285		& 16.767 \\
8192 & 32 & GPU 64 splits			&			& 62.064		& 135.793 \\
12288 & 32 & GPU 256 splits			&			& 196.971	& 460.912 \\
\bottomrule \end{tabular} \\[4pt]
Best timings for R=rectangle, T=triangle, P=parallelogram\footnote{$\le 32$ blocks on my GPU to prevent deadlock}
\end{center}

@@

%\end{document}
